---
title: "Northern Estuaries"
format:
  html:
    toc: true
    dev: png
    type: cairo
encoding: UTF-8
knitr:
  opts_chunk:
    echo: false
    message: false
    warning: false
editor_options: 
  chunk_output_type: console
# execute: 
#   freeze: false
---

```{r date,echo=FALSE,message=FALSE,warning=FALSE}
up.date <- format(Sys.time(),tz="America/New_York",usetz=T,"%F %R")
up.date <- as.POSIXct(up.date,tz="America/New_York")

dst.check=c(NA,FALSE,TRUE)[as.POSIXlt(up.date)$isdst+2]# from lubridate::dst(...) code
```

```{r setup and data}

library(AnalystHelper)
library(reshape2)
library(plyr)
library(sf)
library(EVERSpatDat)
library(mapmisc)
library(flextable)
library(zoo)
# library(tmap)

library(ggplot2)
theme_set(theme_minimal(base_size = 16)+#,base_family = "serif")+
            theme_bw()+
            theme(panel.border = element_rect("black",fill=NA,linewidth=1)))

utm17<-st_crs("EPSG:26917");# CRS for NAD83 UTM17

# tmap_mode("view")
# Functions  ----------------------------------------------------------------
heck_nice <- function(x,round){
      e <- floor(log10(x))
    f <- x/(10^e)
    if (round) {
        if (f < 1.5) 
            nf <- 1
        else if (f < 3) 
            nf <- 2
        else if (f < 7) 
            nf <- 5
        else nf <- 10
    }
    else {
        if (f <= 1) 
            nf <- 1
        else if (f <= 2) 
            nf <- 2
        else if (f <= 5) 
            nf <- 5
        else nf <- 10
    }
    nf * (10^e)
}
heckbert_labs <- function(dmin,dmax,m){
  
    range <- heck_nice((dmax - dmin), FALSE)
    lstep <- heck_nice(range/(m - 1), TRUE)
    lmin <- floor(dmin/lstep) * lstep
    lmax <- ceiling(dmax/lstep) * lstep
    seq(lmin, lmax, by = lstep)
}
# Dates ------------------------------------------------------------------
CurWY      <- WY(date.fun(Sys.time()))
Start.Date <- date.fun(paste(CurWY - 4, "05-01", sep = "-"))
End.Date   <- date.fun(Sys.Date() - 1)
YEST       <- End.Date
dates      <- c(Start.Date, End.Date)
flab.dates <- c(date.fun(paste(CurWY - 15, "05-01", sep = "-")), End.Date)
LOK.sdate  <- date.fun("2007-05-01")

# Plotting constants/colors --------------------------------------------
lok_stage_yrs <- c(CurWY-3,CurWY-2, CurWY-1, CurWY)
lok_stage_cols <- c(adjustcolor(c("purple","forestgreen","blue"), 0.5), "red")

stage_yrs <- c(CurWY-2, CurWY-1, CurWY)
stage_cols <- c(adjustcolor(c("forestgreen","blue"), 0.5), "red")

Q_cols <- c("dodgerblue1","indianred1","forestgreen")

# discharge data --------------------------------------------
Qdbkeys <- readRDS("data/raw/qdbkeys.rds")
Qdbkeys.melt <- reshape(
  Qdbkeys,
  varying = list(c("DA","BK")),# list(names(Qdbkeys)[2:3]), # columns to melt
  v.names = "DBKEY",                   # name for measurement values
  timevar = "freq",                    # name for the new column holding old col names
  times = c("DA","BK"),# names(Qdbkeys)[2:3],         # actual names from original columns
  direction = "long"
)
row.names(Qdbkeys.melt) <- NULL
Qdbkeys.melt <- subset(Qdbkeys.melt,!is.na(DBKEY))

Qdat <- readRDS("data/raw/Qdat.rds")|>
  merge(Qdbkeys.melt,'DBKEY',all.x=T)


```

# Caloosahatchee River Estuary

## Discharge Conditions

```{r CRE Q, echo = FALSE}
CRE_locs <- c("S79","S78","S77")
CRE_Qdat <- subset(Qdat,loc%in%CRE_locs)|>
  dcast(Date+loc~DA_P,value.var = "Data.Value",mean,na.rm=T)

CRE_Qdat$Data.Value <- apply(CRE_Qdat[c("P1","P2")], 1, function(x) x[!is.na(x)][1]);# if more P, just add

# tom_locs<- Qdbkeys[!(Qdbkeys$DA%in%unique(Qdat$DBKEY)),]
CRE_Qdat <- dcast(CRE_Qdat,Date~loc,value.var = "Data.Value", fun.aggregate = function(x) mean(cfs.to.acftd(x),na.rm=T))
CRE_Qdat[is.na(CRE_Qdat)] <- 0; #replace any NAs with 0 

for(col in CRE_locs){
  CRE_Qdat[[paste0(col, ".cfs")]] <- CRE_Qdat[[col]] * (1/cfs.to.acftd(1))
}

CRE_Qdat$S77.cfs <- with(CRE_Qdat,ifelse(S77.cfs<0,0,S77.cfs))
CRE_Qdat$C43 <- with(CRE_Qdat,ifelse(S79.cfs<S77.cfs,0,S79.cfs-S77.cfs))
CRE_Qdat$WY <- WY(CRE_Qdat$Date)
CRE_Qdat$DOWY <- hydro.day(CRE_Qdat$Date)

CRE_Qdat$cum.S79 <- with(CRE_Qdat,ave(S79,WY,FUN = function(x)cumsum(ifelse(is.na(x),0,x))))
CRE_Qdat$cum.S77 <- with(CRE_Qdat,ave(S77,WY,FUN = function(x)cumsum(ifelse(is.na(x),0,x))))
CRE_Qdat$Q.14 <- rollapplyr(CRE_Qdat$S79.cfs,14,mean,na.rm=T,fill=NA)
CRE_Qdat$S79Q.7 <- rollapplyr(CRE_Qdat$S79.cfs,7,mean,na.rm=T,fill=NA)
CRE_Qdat$S77Q.7 <- rollapplyr(CRE_Qdat$S77.cfs,14,mean,na.rm=T,fill=NA)
CRE_Qdat$Q.30 <- rollapplyr(CRE_Qdat$S79.cfs,30,mean,na.rm=T,fill=NA)
CRE_Qdat$SalEnv.cat <- cut(CRE_Qdat$Q.14,
                        breaks = c(-Inf, 750, 2100, 2600, Inf),
                        labels = c("low", "optimum", "stress", "damaging"),
                        right = FALSE
                        )


consec.startend <- function(var) {
  runs <- rle(var)
  idx <- which(runs$values == 1)
  if (length(idx) == 0) return(list(starts = integer(0), ends = integer(0)))
  
  ends <- cumsum(runs$lengths)[idx]
  starts <- ends - runs$lengths[idx] + 1
  list(starts = starts, ends = ends)
}

# Define thresholds for each category
thresholds <- list(
  Low    = function(x) x < 750,
  Opt    = function(x) x >= 750  & x < 2100,
  Stress = function(x) x >= 2100 & x < 2600,
  Dam    = function(x) x >= 2600
)

# Loop over categories to generate binary, consec, and sum.consec columns
for (nm in names(thresholds)) {
  # binary indicator
  CRE_Qdat[[nm]] <- as.integer(thresholds[[nm]](CRE_Qdat$Q.14))
  
  # consecutive marker (1 within consecutive runs, 0 otherwise)
  x <- CRE_Qdat[[nm]]
  CRE_Qdat[[paste0(nm, ".consec")]] <- as.integer(x > 0 & (c(0, head(x, -1)) > 0 | c(0, head(x, -1)) == 0))
  
  # sum of each consecutive run
  consec.val <- consec.startend(CRE_Qdat[[paste0(nm, ".consec")]])
  CRE_Qdat[[paste0("sum.", nm, ".consec")]] <- 0
  if (length(consec.val$ends) > 0) {
    for (i in seq_along(consec.val$ends)) {
      CRE_Qdat[consec.val$ends[i], paste0("sum.", nm, ".consec")] <-
        sum(CRE_Qdat[consec.val$starts[i]:consec.val$ends[i], paste0(nm, ".consec")], na.rm = TRUE)
    }
  }
}


salenv.vals <- subset(CRE_Qdat,Date==max(CRE_Qdat$Date))

salenv.vals1 <- salenv.vals[,paste("sum",c("Low","Opt","Stress","Dam"),"consec",sep=".")]
colnames(salenv.vals1)=c("low","optimal","stress","damaging")

flow.envs <- c("< 750","750 - 2100", "2100 - 2600","> 2600")
env.cols <- c("red","green","orange","red")

```


```{r, CREFlow, echo=FALSE,fig.width=7,fig.height=5,fig.align='center',fig.cap="Daily and 14-day moving average discharge for S-79 relative to the Northern Estuaries RECOVER performance measure for the recent 30-day period."}
max.q <- max(subset(CRE_Qdat,Date%in%seq(date.fun(as.Date(Sys.Date())-30),date.fun(as.Date(Sys.Date())),"1 days"))[,c("S79.cfs","Q.14")],na.rm=T)
ylim.max <- ceiling(max.q*1.2)

ylim.val <- c(0,ylim.max);ymaj <- heckbert_labs(ylim.val[1],ylim.val[2],6);ymin <- seq(ylim.val[1],ylim.val[2],min(diff(ymaj))/2)
xlim.val <- date.fun(c(as.Date(End.Date)-30,as.Date(End.Date)+3));xmaj <- seq(xlim.val[1],xlim.val[2],by="7 days");xmin <- seq(xlim.val[1],xlim.val[2],by="1 days")

layout(matrix(1:2,2,1,byrow=F),widths=c(2,1),heights=c(1,0.5))
par(mar=c(2,2,1,2),oma=c(0.5,3,1,2));
plot(S79.cfs~Date,CRE_Qdat,type="n",ylim=ylim.val,xlim=xlim.val,xaxs="i",yaxs="i",xaxt="n",yaxt="n",xlab=NA,ylab=NA)
xx <- c(xlim.val[1],xlim.val[1],xlim.val[2],xlim.val[2])
yy3 <- c(2600,ylim.max,ylim.max,2600);polygon(x=xx,y=yy3,col=adjustcolor("red",0.5))
yy4 <- c(2100,2600,2600,2100);polygon(x=xx,y=yy4,col=adjustcolor("yellow",0.5))
yy5 <- c(750,2100,2100,750);polygon(x=xx,y=yy5,col=adjustcolor("green",0.5))
abline(h=ymaj,v=xmaj,lty=3,col="grey")
# abline(h=457,col="red")
with(CRE_Qdat,pt_line(Date,S79.cfs,2,"black",1,21,"grey",cex=1.25,pt.lwd=0.1))
with(CRE_Qdat,lines(Date,Q.14,lwd=3,col=adjustcolor("dodgerblue3",0.5)))
axis_fun(1,xmaj,xmin,format(xmaj,"%m/%d/%Y"),line=-0.5)
axis_fun(2,ymaj,ymin,ymaj,cex.axis=1)
axis_fun(4,ymaj,ymin,format(round(cfs.to.acftd(ymaj)/1000,1)),cex.axis=1)

box(lwd=1)
mtext("Date\n(MM/DD/YYYY)",side=1,line=2.75,cex=1)
mtext("Discharge (cfs)",side=2,line=3.5,cex=1)
# mtext("Discharge (kAc-Ft D\u207B\u00B9)",side=4,line=2.5,cex=1.25)
mtext(expression("Daily Discharge (x1000 Ac-Ft d"^" -1"*")"),side=4,line=2.5,cex=1)
plot(0:1,0:1,type="n",yaxt="n",xaxt="n",bty="n")
legend(0.25,0.75,
       legend=c( "Damaging (>2600 cfs)","Stress (2100 - 2600 cfs)","Optimum (750 - 2100 cfs)"),pch=22,
       pt.bg=adjustcolor(c("red","yellow","green"),0.5),pt.cex=2,ncol=1,cex=1,bty="n",y.intersp=1,x.intersp=1,xpd=NA,xjust=0.5,title.adj = 0,title='RECOVER PM')

legend(0.75,0.75,
       legend=c("Daily Discharge (S79)","14-Day moving average"),
       pch=c(21,NA),pt.bg=c("grey",NA),pt.cex=c(1.5,NA),
       lty=c(NA,1),lwd=c(0.5,2),col=c("black",adjustcolor(c("dodgerblue1"),0.5)),
       ncol=1,cex=1,bty="n",y.intersp=1,x.intersp=1,xpd=NA,xjust=0.5,title.adj = 0,title='')

```

**Caloosahatchee Conditions Summary:** Flow to the Caloosahatchee
Estuary had a 7-day average of
**`r format(round(subset(CRE_Qdat,Date==date.fun(as.Date(End.Date)-1))$S79Q.7,0),big.mark=",")`
cfs** at **S-79** with a 7-day average of
**`r format(round(subset(CRE_Qdat,Date==date.fun(as.Date(End.Date)-1))$S77Q.7,0),big.mark=",")`
cfs coming from the lake at** S-77**.** The 14-day moving average flow
at S-79 is `r format(round(salenv.vals$Q.14),big.mark=",")` cfs and has
been in the
**`r paste0("<span style='color:",env.cols[which(salenv.vals1==max(salenv.vals1))],"'>")` `r names(salenv.vals1)[which(salenv.vals1==max(salenv.vals1))]`**
</span> flow envelope
(`r flow.envs[which(salenv.vals1==max(salenv.vals1))]` cfs; RECOVER
2020) for
`r as.numeric(salenv.vals1[which(salenv.vals1==max(salenv.vals1))])`
days.


```{r CRE_LOK_Q, echo=FALSE,fig.width=7,fig.height=4.5,fig.align='center',fig.cap="S-77 (from Lake Okeechobee) and S-79 (to Tidal Basin) flow data along the C-43 and Caloosahatchee River. C-43 Basin Flow was calculated as the difference from S-77 and S-79."}
max.q <- max(subset(CRE_Qdat,Date%in%seq(date.fun(as.Date(Sys.Date())-30),date.fun(as.Date(Sys.Date())),"1 days"))[,c("S79.cfs","S77.cfs","S78.cfs")],na.rm=T)
ylim.max <- ceiling(max.q*1.2)

ylim.val <- c(0,ylim.max);ymaj <- heckbert_labs(ylim.val[1],ylim.val[2],6);ymin <- seq(ylim.val[1],ylim.val[2],min(diff(ymaj))/2)
xlim.val <- date.fun(c(as.Date(End.Date)-30,as.Date(End.Date)+3));xmaj <- seq(xlim.val[1],xlim.val[2],by="7 days");xmin <- seq(xlim.val[1],xlim.val[2],by="1 days")

layout(matrix(1:2,2,1,byrow=F),widths=c(2,1),heights=c(2,0.4))
par(cex.axis=1.2,mar=c(2,2,1,1),oma=c(1,3,1,2));
plot(S79.cfs~Date,CRE_Qdat,type="n",ylim=ylim.val,xlim=xlim.val,xaxs="i",yaxs="i",xaxt="n",yaxt="n",xlab=NA,ylab=NA)
abline(h=ymaj,v=xmaj,lty=3,col="grey")
lines(S79.cfs~Date,CRE_Qdat,col=Q_cols[1],lwd=2)
lines(S77.cfs~Date,CRE_Qdat,col=Q_cols[2],lwd=2,lty=2)
lines(C43~Date,CRE_Qdat,col="black",lwd=2,lty=3)
lines(S78.cfs~Date,CRE_Qdat,col="grey50",lwd=2)
axis_fun(1,xmaj,xmin,format(xmaj,"%m/%d/%Y"),line=-0.5)
axis_fun(2,ymaj,ymin,ymaj,cex.axis=1)
box(lwd=1)
mtext("Date\n(MM/DD/YYYY)",side=1,line=2.75,cex=1)
mtext("Daily Discharge (cfs)",side=2,line=3.5,cex=1)

plot(0:1,0:1,type="n",yaxt="n",xaxt="n",bty="n")
legend(0.5,0.5,
       legend=c("S-79 (to Estuary)","S-77 (from Lake)","C-43 Basin Flow","S-78"),
       col=c(Q_cols[1:2],"black","grey50"),lty=c(1,2,3,1),lwd=2.5,
       pt.cex=2.5,ncol=4,cex=1,bty="n",y.intersp=1,x.intersp=0.5,xpd=NA,xjust=0.5)

```

```{r CRE_cumQ, echo=FALSE,fig.width=7,fig.height=4.5,fig.align='center',fig.cap="Cumulative discharge for S-79 (to Tidal Basin) and S-77 (from Lake Okeechobee) for the last three Florida Water Years (May - April). Day of water year is analogous to day of year with Day 1 = May 1."}
max.q <- max(CRE_Qdat$cum.S79,na.rm=T)
ylim.max <- ceiling(max.q*1.2)

ylim.val <- c(0,ylim.max);ymaj <- heckbert_labs(ylim.val[1],ylim.val[2],6);ymin <- seq(ylim.val[1],ylim.val[2],min(diff(ymaj))/2)
xlim.val=c(0,366);xmaj=seq(xlim.val[1],xlim.val[2],90);xmin=seq(xlim.val[1],xlim.val[2],30)
cum_cols=c("indianred1","orange","dodgerblue1")

layout(matrix(1:2,1,2,byrow=F),widths = c(1,1,0.5))
par(mar=c(2,2,1,1),oma=c(1,3,1,2));

plot(cum.S79~DOWY,CRE_Qdat,type="n",ylim=ylim.val,xlim=xlim.val,xaxs="i",yaxs="i",ann=F,axes=F)
abline(h=ymaj,v=xmaj,lty=3,col="grey")
for(i in 1:3){
  if(i==3){
    lines(cum.S79~DOWY,subset(CRE_Qdat,WY==seq(CurWY-2,CurWY,1)[i]),lwd=2.5,col=cum_cols[i])}
  else{
    lines(cum.S79~DOWY,subset(CRE_Qdat,WY==seq(CurWY-2,CurWY,1)[i]),lwd=3,col=adjustcolor(cum_cols[i],0.5))
    }
}
axis_fun(1,xmaj,xmin,xmaj,line=-0.5)
axis_fun(2,ymaj,ymin,ymaj/1000,cex.axis=1);box(lwd=1)
mtext("Day of Water Year",side=1,line=2,cex=1)
mtext(expression("Cumulative Discharge (x1000 Ac-Ft WY"^" -1"*")"),side=2,line=3.5,cex=1)
mtext(side=3,"S-79",adj=0)

plot(cum.S77~DOWY,CRE_Qdat,type="n",ylim=ylim.val,xlim=xlim.val,xaxs="i",yaxs="i",ann=F,axes=F)
abline(h=ymaj,v=xmaj,lty=3,col="grey")
for(i in 1:3){
  if(i==3){
    lines(cum.S77~DOWY,subset(CRE_Qdat,WY==seq(CurWY-2,CurWY,1)[i]),lwd=2.5,col=cum_cols[i])}
  else{
    lines(cum.S77~DOWY,subset(CRE_Qdat,WY==seq(CurWY-2,CurWY,1)[i]),lwd=3,col=adjustcolor(cum_cols[i],0.5))
  }
}
axis_fun(1,xmaj,xmin,xmaj,line=-0.5)
axis_fun(2,ymaj,ymin,NA);box(lwd=1)
mtext("Day of Water Year",side=1,line=2,cex=1)
mtext(side=3,"S-77",adj=0)

#plot(0:1,0:1,type="n",yaxt="n",xaxt="n",bty="n")
legend("topright",
       legend=c(paste0("WY",seq(CurWY-2,CurWY,1))),
       col=cum_cols,lty=c(1),lwd=c(2.5),pt.cex=1,ncol=1,cex=1,bty="n",y.intersp=1,x.intersp=0.5,xpd=NA,xjust=0.5)
```

## Salinity

```{r sal data,echo = FALSE}
sal_dat <- readRDS("data/raw/sal_dat.rds")
sal_dat_xtab <- dcast(sal_dat,loc+Date~param,value.var = "Data.Value",mean,na.rm=TRUE)
sal_dat_xtab$calc_Sal <- with(sal_dat_xtab,
                              ifelse(is.na(SAL),SalinityCalc(SPC,WT),SAL))
sal_dat_xtab$DOY <- as.numeric(format(sal_dat_xtab$Date,"%j"))
sal_dat_xtab$DOWY <- hydro.day(sal_dat_xtab$Date)
sal_dat_xtab$WY <- WY(sal_dat_xtab$Date)
```


```{r CRE_Sal,echo=FALSE,fig.width=10,fig.height=5,fig.align='center',fig.cap="Daily average bottom salinity data for the last 14-days from sampling locations within the tidal Caloosahatchee River Estuary relative to oyster health (Sanibel, Shell Point and Cape Coral) and tape grass (<i>Vallisneria americana</i>) health (Ft. Myers only) conditions."}
CALSITES <- c("SANIB2","MARKH","CCORAL","FORTMYERSM","S79")
cre_sal <- subset(sal_dat_xtab,loc%in%CALSITES)

fill <- expand.grid(loc=CALSITES,Date=date.fun(seq(Start.Date[1],YEST,"1 days")))
fill$DOY <- as.numeric(format(fill$Date,"%j"))
fill$DOWY <- hydro.day(fill$Date)
fill$WY <- WY(fill$Date)
cre_sal <- merge(cre_sal,fill,c("loc","Date","DOY","DOWY","WY"),all.y=T)

## removed daily sample number screening
cre_sal$MovingAvg.7d=with(cre_sal,ave(calc_Sal,loc,FUN=function(x) rollapplyr(x,7,mean,fill=NA)))

xlim.val <- date.fun(c(as.Date(End.Date)-30,as.Date(End.Date)+3));xmaj <- seq(xlim.val[1],xlim.val[2],by="7 days");xmin <- seq(xlim.val[1],xlim.val[2],by="1 days")
ylim.val <- c(0,max(cre_sal$calc_Sal,na.rm=T)*1.10);
ylim.val2 <- c(0,20);
by.y <- 10;ymaj <- seq(ylim.val[1],ylim.val[2],by.y);ymin=seq(ylim.val[1],ylim.val[2],by.y/2)
colrmp <- "blue"
txt.cex <- 1
par(mar=c(1.5,2,1,1),oma=c(2,3,4,1));
layout(matrix(c(1:4,rep(5,3),6),2,4,byrow=T),heights=c(1,0.25));

station.label=c("Sanibel","Shell Point","Cape Coral","Ft. Myers")
recon.lab=c("Tarpon Bay","Shell Point",NA,"Ft. Myers")
for(i in 1:3){
  plot(calc_Sal~Date,subset(cre_sal,loc==CALSITES[i]),type="n",ylim=ylim.val,xlim=xlim.val,xaxs="i",yaxs="i",ann=F,axes=F)
  xx <- c(xlim.val[1],xlim.val[1],xlim.val[2],xlim.val[2])
  yy <- c(0,5,5,0);polygon(x=xx,y=yy,col="peachpuff1")
  yy2 <- c(35,ylim.val[2],ylim.val[2],35);polygon(x=xx,y=yy2,col="peachpuff1")
  yy3 <- c(30,35,35,30);polygon(x=xx,y=yy3,col="khaki")
  yy4 <- c(5,10,10,5);polygon(x=xx,y=yy4,col="khaki")
  yy5 <- c(10,30,30,10);polygon(x=xx,y=yy5,col="darkseagreen2")
  abline(h=seq(0,40,5))
  with(subset(cre_sal,loc==CALSITES[i]),pt_line(Date,calc_Sal,1,colrmp,2,21,colrmp,cex=2,pt.col=colrmp))
  with(subset(cre_sal,loc==CALSITES[i]),lines(Date,MovingAvg.7d,lwd=2.5,col="orange"))
  axis_fun(1,xmaj,xmin,format(xmaj,"%m/%d"),line=-0.5)
  axis_fun(2,ymaj,ymin,ymaj)
  mtext(side=3,station.label[i])
  box(lwd=1)
  if(i==1){mtext(side=2,"Salinity (PSU)",line=2,cex=1)}
  if(i==2){mtext(expression(paste(underline("Oyster Condition"))),side=3,cex=1,line=1.75,outer=F)}
}

plot(calc_Sal~Date,subset(cre_sal,loc==CALSITES[i]),type="n",ylim=ylim.val,xlim=xlim.val,xaxs="i",yaxs="i",ann=F,axes=F)
xx=c(xlim.val[1],xlim.val[1],xlim.val[2],xlim.val[2])
yy=c(0,10,10,0);polygon(x=xx,y=yy,col="darkseagreen2")
yy=c(10,15,15,10);polygon(x=xx,y=yy,col="khaki")
yy=c(15,ylim.val[2],ylim.val[2],15);polygon(x=xx,y=yy,col="peachpuff1")
abline(h=seq(0,40,5))
with(subset(cre_sal,loc==CALSITES[4]),pt_line(Date,calc_Sal,1,colrmp,2,21,colrmp,cex=2,pt.col=colrmp))
with(subset(cre_sal,loc==CALSITES[4]),lines(Date,MovingAvg.7d,lwd=2.5,col="orange"))
axis_fun(1,xmaj,xmin,format(xmaj,"%m/%d"),line=-0.5)
axis_fun(2,ymaj,ymin,ymaj)
mtext(side=3,station.label[4])
box(lwd=1)
mtext("Month/Day",side=1,line=-6,cex=1,outer=T)
mtext(expression(paste(underline("Tape grass Condition"))),side=3,cex=1,line=1.75,outer=F)

plot(0:1,0:1,ann=F,axes=F,type="n")

legend(0.25,0.15,legend=c("Daily Average", "7-Day Moving Avg"),
       pch=c(21,NA),
       lty=c(NA,1),
       lwd=c(0.01,3),
       col=c("blue","orange"),
       pt.bg=c("blue",NA),
       pt.cex=1.5,ncol=1,cex=1.25,bty="n",y.intersp=1,x.intersp=0.75,xpd=NA,xjust=0.5,yjust=0.5,
       title.adj = 0,title="")
legend(0.5,0.15,legend=c("Poor(<5 or >35)","Fair (5-10 or 30-35)","Good(10-30)"),
       pch=c(22,22,22),
       lty=NA,
       lwd=0.01,
       col="black",
       pt.bg=c("peachpuff1","khaki","darkseagreen2"),
       pt.cex=2.5,ncol=1,cex=1.25,bty="n",y.intersp=1,x.intersp=0.75,xpd=NA,xjust=0.5,yjust=0.5,
       title.adj = 0,title="Oyster Salinity Condition")

plot(0:1,0:1,ann=F,axes=F,type="n")
legend(0.5,0.15,legend=c("Poor(>15)","Fair (10 - 15)","Good(<10)"),
       pch=c(22,22,22),
       lty=NA,
       lwd=0.01,
       col="black",
       pt.bg=c("peachpuff1","khaki","darkseagreen2"),
       pt.cex=2.5,ncol=1,cex=1.25,bty="n",y.intersp=1,x.intersp=0.75,xpd=NA,xjust=0.5,yjust=0.5,
       title.adj = 0,title="Tape Grass Salinity Condition")

# dev.off()
```

<br>

------------------------------------------------------------------------

# St Lucie River Estuary

## Discharge Conditions
```{r SLE Q,include =FALSE}
SLE_locs <- c("GORDY","S49","S48","S80","S308")
SLE_Qdat <- subset(Qdat,loc%in%SLE_locs)|>
  dcast(Date+loc~DA_P,value.var = "Data.Value",mean,na.rm=T)

SLE_Qdat$Data.Value <- SLE_Qdat$P1
#  SLE_Qdat$Data.Value <- apply(SLE_Qdat[c("P1","P2")], 1, function(x) x[!is.na(x)][1]);  
SLE_Qdat <- dcast(SLE_Qdat,Date~loc,value.var = "Data.Value", fun.aggregate = function(x) mean(cfs.to.acftd(x),na.rm=T))
SLE_Qdat[is.na(SLE_Qdat)] <- 0; #replace any NAs with 0 


for(col in SLE_locs){
  SLE_Qdat[[paste0(col, ".cfs")]] <- SLE_Qdat[[col]] * (1/cfs.to.acftd(1))
}

SLE_Qdat$C44 <- with(SLE_Qdat,ifelse(S80.cfs<S308.cfs,0,S80.cfs-S308.cfs))
SLE_Qdat$NorthFork <- apply(SLE_Qdat[,c("GORDY.cfs","S49.cfs","S48.cfs")],1,sum,na.rm=T)

SLE_Qdat$SLE.tot <- apply(SLE_Qdat[,c("GORDY.cfs","S49.cfs","S48.cfs","S80.cfs")],1,sum,na.rm=T)
SLE_Qdat$Q.14 <- rollapplyr(SLE_Qdat$SLE.tot,14,mean,fill=NA)
SLE_Qdat$Q.7 <- rollapplyr(SLE_Qdat$SLE.tot,7,mean,fill=NA)
SLE_Qdat$S308Q.7 <- rollapplyr(SLE_Qdat$S308.cfs,7,mean,fill=NA)
SLE_Qdat$WY <- WY(SLE_Qdat$Date)
SLE_Qdat$DOWY <- hydro.day(SLE_Qdat$Date)

SLE_Qdat$cum.S80 <- with(SLE_Qdat,ave(S80,WY,FUN = function(x)cumsum(ifelse(is.na(x),0,x))))
SLE_Qdat$cum.S308 <- with(SLE_Qdat,ave(S308,WY,FUN = function(x)cumsum(ifelse(is.na(x),0,x))))
SLE_Qdat$cum.S308pos <- with(SLE_Qdat,ave(S308,WY,FUN = function(x)cumsum(ifelse(is.na(x),0,ifelse(x<0,0,x)))))

```

```{r, SLEFlow, echo=FALSE,fig.width=7,fig.height=5,fig.align='center',fig.cap="Daily and 14-day moving average discharge for north and south fork relative to the Northern Estuaries RECOVER performance measure for the recent 30-day period."}
max.q <- max(subset(SLE_Qdat,Date%in%seq(date.fun(as.Date(Sys.Date())-30),date.fun(as.Date(Sys.Date())),"1 days"))[,c("SLE.tot","Q.14")],na.rm=T)
ylim.max <- ceiling(max.q*1.2)

ylim.val <- c(0,ylim.max);ymaj <- heckbert_labs(ylim.val[1],ylim.val[2],6);ymin <- seq(ylim.val[1],ylim.val[2],min(diff(ymaj))/2)
xlim.val <- date.fun(c(as.Date(End.Date)-30,as.Date(End.Date)+3));xmaj <- seq(xlim.val[1],xlim.val[2],by="7 days");xmin <- seq(xlim.val[1],xlim.val[2],by="1 days")

layout(matrix(1:2,2,1,byrow=F),widths=c(2,1),heights=c(1,0.5))
par(mar=c(2,2,1,2),oma=c(0.5,3,1,2));
plot(S80.cfs~Date,SLE_Qdat,type="n",ylim=ylim.val,xlim=xlim.val,xaxs="i",yaxs="i",xaxt="n",yaxt="n",xlab=NA,ylab=NA)
xx <- c(xlim.val[1],xlim.val[1],xlim.val[2],xlim.val[2])
yy3 <- c(1700,ylim.max,ylim.max,1700);polygon(x=xx,y=yy3,col=adjustcolor("red",0.5))
yy4 <- c(1400,1700,1700,1400);polygon(x=xx,y=yy4,col=adjustcolor("yellow",0.5))
yy5 <- c(150,1400,1400,150);polygon(x=xx,y=yy5,col=adjustcolor("green",0.5))
abline(h=ymaj,v=xmaj,lty=3,col="grey")
with(SLE_Qdat,pt_line(Date,SLE.tot,2,"black",1,21,"grey",cex=1.25,pt.lwd=0.1))
with(SLE_Qdat,lines(Date,Q.14,lwd=3,col=adjustcolor("dodgerblue3",0.5)))
axis_fun(1,xmaj,xmin,format(xmaj,"%m/%d/%Y"),line=-0.5)
axis_fun(2,ymaj,ymin,ymaj,cex.axis=1)
axis_fun(4,ymaj,ymin,format(round(cfs.to.acftd(ymaj)/1000,1)),cex.axis=1)
mtext(side=3,line=-1.25,adj=0,col="white"," Does not include coastal run-off",cex=0.95,font=2)

box(lwd=1)
mtext("Date\n(MM/DD/YYYY)",side=1,line=2.75,cex=1)
mtext("Discharge (cfs)",side=2,line=3.5,cex=1)
# mtext("Discharge (kAc-Ft D\u207B\u00B9)",side=4,line=2.5,cex=1.25)
mtext(expression("Daily Discharge (x1000 Ac-Ft d"^" -1"*")"),side=4,line=2.5,cex=1)
plot(0:1,0:1,type="n",yaxt="n",xaxt="n",bty="n")
legend(0.1,0.75,
       legend=c( "Damaging (>1700 cfs)","Stress (1400 - 1700 cfs)","Optimum (150 - 1400 cfs)"),
       pch=22,pt.bg=adjustcolor(c("red","yellow","green"),0.5),pt.cex=2,
       ncol=1,cex=1,bty="n",y.intersp=1,x.intersp=1,xpd=NA,xjust=0.5,title.adj = 0,title='RECOVER PM')
legend(0.75,0.75,
       legend=c("Daily Discharge (S79)","14-Day moving average"),
       pch=c(21,NA),pt.bg=c("grey",NA),pt.cex=c(1.5,NA),
       lty=c(NA,1),lwd=c(0.5,2),col=c("black",adjustcolor(c("dodgerblue1"),0.5)),
       ncol=1,cex=1,bty="n",y.intersp=1,x.intersp=1,xpd=NA,xjust=0.5,title.adj = 0,title='')
```

**St Lucie Conditions Summary:** Flow to the St Lucie Estuary had a
7-day average of
**`r format(round(subset(SLE_Qdat,Date==date.fun(as.Date(End.Date)-1))$Q.7,0),big.mark=",")`
cfs** from **North and South Forks** with a 7-day average of
**`r format(round(subset(SLE_Qdat,Date==date.fun(as.Date(End.Date)-1))$S308Q.7,0),big.mark=",")`
cfs** coming from the lake at **S-308**.

```{r SLE_LOK_Q, echo=FALSE,fig.width=6,fig.height=4.5,fig.align='center',fig.cap="S-308 (from Lake Okeechobee), S-80 (to Lower Fork),  C-44 Basin and North Fork (Gordy Rd, S49, S48) daily discharge. C-44 Basin Flow was calculated as the difference from S-308 and S-80."}
max.q <- max(subset(SLE_Qdat,Date%in%seq(date.fun(as.Date(Sys.Date())-30),date.fun(as.Date(Sys.Date())),"1 days"))[,c("S80.cfs","NorthFork","S308.cfs")],na.rm=T)
ylim.max <- ceiling(max.q*1.2)

ylim.val <- c(0,ylim.max);ymaj <- heckbert_labs(ylim.val[1],ylim.val[2],6);ymin <- seq(ylim.val[1],ylim.val[2],min(diff(ymaj))/2)
xlim.val <- date.fun(c(as.Date(End.Date)-30,as.Date(End.Date)+3));xmaj <- seq(xlim.val[1],xlim.val[2],by="7 days");xmin <- seq(xlim.val[1],xlim.val[2],by="1 days")

SLE_Q_cols <- c("dodgerblue1","indianred1","black","lightgreen")

layout(matrix(1:2,2,1,byrow=F),widths=c(2,1),heights=c(2,0.4))
par(mar=c(2,2,1,1),oma=c(1,3,1,2));
plot(S80~Date,SLE_Qdat,type="n",ylim=ylim.val,xlim=xlim.val,xaxs="i",yaxs="i",ann=FALSE,axes=FALSE)
abline(h=ymaj,v=xmaj,lty=3,col="grey")
with(SLE_Qdat,lines(Date,S80.cfs,col=SLE_Q_cols[1],lwd=2))
with(SLE_Qdat,lines(Date,S308.cfs,col=SLE_Q_cols[2],lwd=2,lty=2))
with(SLE_Qdat,lines(Date,C44,col=SLE_Q_cols[3],lwd=2,lty=3))
with(SLE_Qdat,lines(Date,NorthFork,col=SLE_Q_cols[4],lwd=2,lty=1))
axis_fun(1,xmaj,xmin,format(xmaj,"%m/%d/%Y"),line=-0.5)
axis_fun(2,ymaj,ymin,format(ymaj),cex.axis=1)
box(lwd=1)
mtext("Date\n(MM/DD/YYYY)",side=1,line=2.75,cex=1)
mtext("Daily Discharge (cfs)",side=2,line=3.5,cex=1)

plot(0:1,0:1,type="n",yaxt="n",xaxt="n",bty="n")
legend(0.5,0.6,
       legend=c("S-80 (to Estuary)","S-308 (from Lake)","C-44 Basin Flow","North Fork"),
       col=SLE_Q_cols,lty=c(1,2,3,1),lwd=c(2,2,2,2),pt.cex=2,ncol=2,cex=1,bty="n",y.intersp=1,x.intersp=0.5,xpd=NA,xjust=0.5)

```

<br>

```{r SLE_cumQ, echo=FALSE,fig.width=7,fig.height=4.5,fig.align='center',fig.cap="Cumulative discharge for S-80 (to Tidal Basin) and S-308 (from Lake Okeechobee) for the last three Florida Water Years (May - April). Day of water year is analogous to day of year with Day 1 = May 1."}
max.q <- max(SLE_Qdat$cum.S80,na.rm=T)
ylim.max <- ceiling(max.q*1.2)

ylim.val <- c(0,ylim.max);ymaj <- heckbert_labs(ylim.val[1],ylim.val[2],6);ymin <- seq(ylim.val[1],ylim.val[2],min(diff(ymaj))/2)
xlim.val=c(0,366);xmaj=seq(xlim.val[1],xlim.val[2],90);xmin=seq(xlim.val[1],xlim.val[2],30)
cum_cols=c("indianred1","orange","dodgerblue1")

layout(matrix(1:2,1,2,byrow=F),widths = c(1,1,0.5))
par(mar=c(2,2,1,1),oma=c(1,3,1,2));

plot(cum.S80~DOWY,SLE_Qdat,type="n",ylim=ylim.val,xlim=xlim.val,xaxs="i",yaxs="i",ann=F,axes=F)
abline(h=ymaj,v=xmaj,lty=3,col="grey")
for(i in 1:3){
  if(i==3){
    lines(cum.S80~DOWY,subset(SLE_Qdat,WY==seq(CurWY-2,CurWY,1)[i]),lwd=2.5,col=cum_cols[i])}
  else{
    lines(cum.S80~DOWY,subset(SLE_Qdat,WY==seq(CurWY-2,CurWY,1)[i]),lwd=3,col=adjustcolor(cum_cols[i],0.5))
  }
}
axis_fun(1,xmaj,xmin,xmaj,line=-0.5)
axis_fun(2,ymaj,ymin,ymaj/1000,cex.axis=1);box(lwd=1)
mtext("Day of Water Year",side=1,line=2,cex=1)
mtext(expression("Cumulative Discharge (x1000 Ac-Ft WY"^" -1"*")"),side=2,line=3.5,cex=1)
mtext(side=3,"S-80",adj=0)

plot(cum.S308pos~DOWY,SLE_Qdat,type="n",ylim=ylim.val,xlim=xlim.val,xaxs="i",yaxs="i",ann=F,axes=F)
abline(h=ymaj,v=xmaj,lty=3,col="grey")
for(i in 1:3){
  if(i==3){
    lines(cum.S308pos~DOWY,subset(SLE_Qdat,WY==seq(CurWY-2,CurWY,1)[i]),lwd=2.5,col=cum_cols[i])}
  else{
    lines(cum.S308pos~DOWY,subset(SLE_Qdat,WY==seq(CurWY-2,CurWY,1)[i]),lwd=3,col=adjustcolor(cum_cols[i],0.5))
  }
}
axis_fun(1,xmaj,xmin,xmaj,line=-0.5)
axis_fun(2,ymaj,ymin,NA);box(lwd=1)
mtext("Day of Water Year",side=1,line=2,cex=1)
mtext(side=3,"S-308",adj=0)
mtext(side=3,line=-1," positive flow only",adj=0,cex=0.9,font=3)

#plot(0:1,0:1,type="n",yaxt="n",xaxt="n",bty="n")
legend("topright",
       legend=c(paste0("WY",seq(CurWY-2,CurWY,1))),
       col=cum_cols,lty=c(1),lwd=c(2.5),pt.cex=1,ncol=1,cex=1,bty="n",y.intersp=1,x.intersp=0.5,xpd=NA,xjust=0.5)

```

## Salinity

```{r SLE Sal,include = FALSE}
STLSITES <- c("HR1","STL_RIVER","STL_STPT")
station.label <- c("HR1","US1","A1A")
sle_sal <- subset(sal_dat_xtab,loc%in%STLSITES)

sle_sal$loc <- as.factor(sle_sal$loc)

# fill <- expand.grid(SITE=STLSITES,Date=date.fun(seq(Start.Date[1],YEST,"1 days")))
# fill$DOY <- as.numeric(format(fill$Date,"%j"))
# fill$DOWY <- as.numeric(hydro.day(fill$Date))
# fill$WY <- WY(fill$Date)
# sle_sal <- merge(sle_sal,fill,c("SITE","Date","DOY","DOWY","WY"),all.y=T)

## removed daily sample number screening
sle_sal$MovingAvg.7d=with(sle_sal,ave(calc_Sal,loc,FUN=function(x) rollapplyr(x,7,mean,fill=NA)))

```

```{r SLE_Sal,echo=FALSE,fig.width=10,fig.height=5,fig.align='center',fig.cap="Daily average bottom salinity data for the last 14-days from sampling locations within the tidal St Lucie River Estuary relative to oyster health conditions."}

# fill <- expand.grid(SITE=STLSITES,Date=date.fun(seq(Start.Date[1],YEST,"1 days")))
# fill$DOY <- as.numeric(format(fill$Date,"%j"))
# fill$DOWY <- as.numeric(hydro.day(fill$Date))
# fill$WY <- WY(fill$Date)
# sle_sal <- merge(sle_sal,fill,c("SITE","Date","DOY","DOWY","WY"),all.y=T)

## removed daily sample number screening
xlim.val <- date.fun(c(as.Date(End.Date)-30,as.Date(End.Date)+3));xmaj <- seq(xlim.val[1],xlim.val[2],by="7 days");xmin <- seq(xlim.val[1],xlim.val[2],by="1 days")
ylim.val <- c(0,40);
by.y <- 10;ymaj=seq(ylim.val[1],ylim.val[2],by.y);ymin=seq(ylim.val[1],ylim.val[2],by.y/2)
colrmp="blue"
txt.cex=1
par(mar=c(1.5,2,1,1),oma=c(2,3,4,1));
layout(matrix(c(1:3,rep(4,3)),2,3,byrow=T),heights=c(1,0.25));
for(i in 1:3){
  plot(calc_Sal~Date,subset(sle_sal,loc==STLSITES[i]),type="n",ylim=ylim.val,xlim=xlim.val,xaxs="i",yaxs="i",ann=F,axes=F)
  xx <- c(xlim.val[1],xlim.val[1],xlim.val[2],xlim.val[2])
  yy <- c(0,5,5,0);polygon(x=xx,y=yy,col="peachpuff1")
  yy2 <- c(35,40,40,35);polygon(x=xx,y=yy2,col="peachpuff1")
  yy3 <- c(30,35,35,30);polygon(x=xx,y=yy3,col="khaki")
  yy4 <- c(5,10,10,5);polygon(x=xx,y=yy4,col="khaki")
  yy5 <- c(10,30,30,10);polygon(x=xx,y=yy5,col="darkseagreen2")
  abline(h=seq(0,40,5))
  with(subset(sle_sal,loc==STLSITES[i]),pt_line(Date,calc_Sal,1,colrmp,2,21,colrmp,cex=2,pt.col=colrmp))
  with(subset(sle_sal,loc==STLSITES[i]),lines(Date,MovingAvg.7d,lwd=2.5,col="orange"))
  axis_fun(1,xmaj,xmin,format(xmaj,"%m/%d"),line=-0.5)
  axis_fun(2,ymaj,ymin,ymaj)
  mtext(side=3,station.label[i])
  box(lwd=1)
  if(i==1){mtext(side=2,"Salinity (PSU)",line=2,cex=1)}
  if(i==2){mtext(expression(paste(underline("Oyster Condition"))),side=3,cex=1,line=1.75,outer=F)}
}
mtext("Month/Day",side=1,line=-6,cex=1,outer=T)
plot(0:1,0:1,ann=F,axes=F,type="n")
# mtext(side=3,line=-1.25,"Date (Month/Day)")
legend(0.25,0.15,legend=c("Daily Average", "7-Day Moving Avg"),
       pch=c(21,NA),
       lty=c(NA,1),
       lwd=c(0.01,3),
       col=c("blue","orange"),
       pt.bg=c("blue",NA),
       pt.cex=1.5,ncol=1,cex=1.25,bty="n",y.intersp=1,x.intersp=0.75,xpd=NA,xjust=0.5,yjust=0.5,
       title.adj = 0,title="")
legend(0.75,0.15,legend=c("Poor(<5 or >35)","Fair (5-10 or 30-35)","Good(10-30)"),
       pch=c(22,22,22),
       lty=NA,
       lwd=0.01,
       col="black",
       pt.bg=c("peachpuff1","khaki","darkseagreen2"),
       pt.cex=2.5,ncol=1,cex=1.25,bty="n",y.intersp=1,x.intersp=0.75,xpd=NA,xjust=0.5,yjust=0.5,
       title.adj = 0,title="Oyster Salinity Condition")

  
```

------------------------------------------------------------------------

*Page rendered: `r format(Sys.time(), "%b %d, %Y %H:%M %Z")`  •  Data through: `r format(YEST, "%b %d, %Y")`*