---
title: "Lake Okeechobee"
format:
  html:
    toc: true
    dev: png
    type: cairo
encoding: UTF-8
knitr:
  opts_chunk:
    echo: false
    message: false
    warning: false
editor_options: 
  chunk_output_type: console
# execute: 
#   freeze: false
---

```{r date,echo=FALSE,message=FALSE,warning=FALSE}
up.date <- format(Sys.time(),tz="America/New_York",usetz=T,"%F %R")
up.date <- as.POSIXct(up.date,tz="America/New_York")

dst.check=c(NA,FALSE,TRUE)[as.POSIXlt(up.date)$isdst+2]# from lubridate::dst(...) code
# knitr::opts_chunk$set(echo=FALSE,
#                       message=FALSE,
#                       warning=FALSE,
#                       fig.path="_site/images/",
#                       dpi=200)

## Turn on/off LOK recovery envelope shading
RecEnv.plot  <-  0
rec.ops <-  0
```

`r paste("Updated:",up.date, ifelse(dst.check==T,"EDT","EST"))`

```{r setup and data}

library(AnalystHelper)
library(reshape2)
library(plyr)
library(sf)
library(EVERSpatDat)
library(mapmisc)
library(flextable)
# library(tmap)

library(ggplot2)
theme_set(theme_minimal(base_size = 16)+#,base_family = "serif")+
            theme_bw()+
            theme(panel.border = element_rect("black",fill=NA,linewidth=1)))

utm17<-st_crs("EPSG:26917");# CRS for NAD83 UTM17

# tmap_mode("view")
# Functions  ----------------------------------------------------------------
heck_nice <- function(x,round){
      e <- floor(log10(x))
    f <- x/(10^e)
    if (round) {
        if (f < 1.5) 
            nf <- 1
        else if (f < 3) 
            nf <- 2
        else if (f < 7) 
            nf <- 5
        else nf <- 10
    }
    else {
        if (f <= 1) 
            nf <- 1
        else if (f <= 2) 
            nf <- 2
        else if (f <= 5) 
            nf <- 5
        else nf <- 10
    }
    nf * (10^e)
}
heckbert_labs <- function(dmin,dmax,m){
  
    range <- heck_nice((dmax - dmin), FALSE)
    lstep <- heck_nice(range/(m - 1), TRUE)
    lmin <- floor(dmin/lstep) * lstep
    lmax <- ceiling(dmax/lstep) * lstep
    seq(lmin, lmax, by = lstep)
}
# Dates ------------------------------------------------------------------
CurWY      <- WY(date.fun(Sys.time()))
Start.Date <- date.fun(paste(CurWY - 4, "05-01", sep = "-"))
End.Date   <- date.fun(Sys.Date() - 1)
YEST       <- End.Date
dates      <- c(Start.Date, End.Date)
flab.dates <- c(date.fun(paste(CurWY - 15, "05-01", sep = "-")), End.Date)
LOK.sdate  <- date.fun("2007-05-01")

# Plotting constants/colors --------------------------------------------
lok_stage_yrs <- c(CurWY-3,CurWY-2, CurWY-1, CurWY)
lok_stage_cols <- c(adjustcolor(c("purple","forestgreen","blue"), 0.5), "red")

stage_yrs <- c(CurWY-2, CurWY-1, CurWY)
stage_cols <- c(adjustcolor(c("forestgreen","blue"), 0.5), "red")

Q_cols <- c("dodgerblue1","indianred1","forestgreen")

## Schedule/envelopes --------------------------------------------------
vals <- c(-3, -2, -1, 0, 1)
sch_fill <- data.frame(Date=seq(date.fun(paste(CurWY+min(vals),"01-01",sep="-")),date.fun(paste(CurWY+max(vals),"04-30",sep="-")),"1 days"))

LORS08.sch.bk <- data.frame(
  day = c(1, 2, 2, 16, 2, 1, 2, 2, 16, 2, 1, 1, 1, 16, 2, 1, 1, 1, 16, 2, 1, 
          16, 16, 1, 16, 1, 1, 1, 16, 1, 16, 1, 16, 1, 2, 1, 1, 16, 1, 16, 1,
          16, 1, 2, 1, 1, 2, 2, 1, 1, 1, 1, 2, 1, 2, 1, 1), 
  month = c(1, 4, 6, 9, 11, 1, 4, 6, 9, 11, 1, 4, 6, 9, 11, 1, 4, 6, 9, 11, 
            1, 2, 4, 6, 9, 10, 12, 1, 2, 4, 4, 6, 9, 10, 11, 12, 1, 2, 4, 4,
            6, 9, 10, 11, 12, 1, 9, 10, 1, 4, 5, 6, 6, 10, 10, 11, 12),
  variable = c("ZONE.B", "ZONE.B", "ZONE.B", "ZONE.B", "ZONE.B", "ZONE.C", 
               "ZONE.C", "ZONE.C", "ZONE.C", "ZONE.C", "ZONE.C1", "ZONE.C1",
               "ZONE.C1", "ZONE.C1", "ZONE.C1", "ZONE.D", "ZONE.D", "ZONE.D", 
               "ZONE.D", "ZONE.D", "ZONE.D0", "ZONE.D0", "ZONE.D0", "ZONE.D0",
               "ZONE.D0", "ZONE.D0", "ZONE.D0", "ZONE.D1", "ZONE.D1", 
               "ZONE.D1", "ZONE.D1", "ZONE.D1", "ZONE.D1", "ZONE.D1",
               "ZONE.D1", "ZONE.D1", "ZONE.D2", "ZONE.D2", "ZONE.D2", 
               "ZONE.D2", "ZONE.D2", "ZONE.D2", "ZONE.D2", "ZONE.D2",
               "ZONE.D2", "ZONE.E", "ZONE.E", "ZONE.E", "ZONE.SSM",
               "ZONE.SSM", "ZONE.SSM", "ZONE.SSM", "ZONE.SSM", "ZONE.SSM",
               "ZONE.SSM", "ZONE.SSM", "ZONE.SSM"), 
  value = c(17.25, 17.25, 16, 16.5, 17.25, 16.88, 16.5, 15.5, 16.13, 16.88, 
            15.25, 14.5, 14, 14.75, 15.25, 16.25, 15.5, 15, 15.75, 16.25, 14,
            13.5, 13.5, 13, 14, 14.5, 14.5, 14.75, 14.29, 14.17, 14.13, 13.67,
            14.58, 14.97, 15.08, 15.08, 15.5, 15.08, 14.83, 14.75, 14.33, 
            15.17, 15.44, 15.67, 15.67, 12.6, 12.6, 13, 12.16, 11.7, 10.95, 
            10.5, 10.5, 13, 13, 12.8, 12.4))  
LOSOM.sch.bk <- data.frame(
  day = c(1, 2, 2, 2, 1, 2, 2, 1, 2, 2, 1, 1, 1, 1, 2, 1, 2, 1, 1, 1, 1, 1,
          1, 2, 22, 2, 2, 1, 1, 1, 1, 2, 2, 2, 1, 1, 1, 1, 2, 1, 2, 1, 1), 
  month = c(1, 4, 6, 11, 1, 6, 11, 1, 6, 11, 1, 4, 5, 6, 6, 10, 10, 11, 12,
            1, 4, 5, 6, 6, 8, 10, 11, 1, 4, 5, 6, 6, 10, 11, 1, 4, 5, 6, 6,
            10, 10, 11, 12), 
  variable = c("ZONE.A", "ZONE.A", "ZONE.A", "ZONE.A", "ZONE.BC", "ZONE.BC", 
               "ZONE.BC",  "ZONE.BXX", "ZONE.BXX", "ZONE.BXX", "ZONE.D",
               "ZONE.D", "ZONE.D",  "ZONE.D", "ZONE.D", "ZONE.D", "ZONE.D",
               "ZONE.D", "ZONE.D", "ZONE.D1",  "ZONE.D1", "ZONE.D1", "ZONE.D1", 
               "ZONE.D1", "ZONE.D1", "ZONE.D1", "ZONE.D1", "ZONE.D2", 
               "ZONE.D2", "ZONE.D2", "ZONE.D2", "ZONE.D2", "ZONE.D2",
               "ZONE.D2", "ZONE.D3", "ZONE.D3", "ZONE.D3", "ZONE.D3",
               "ZONE.D3", "ZONE.D3", "ZONE.D3", "ZONE.D3", "ZONE.D3"), 
  value = c(17.25, 17.25, 16.5, 17.25, 16.85, 16.1, 16.85, 16.85, 16.1, 16.85,
            12.16,  11.7, 10.95, 10.5, 10.5, 13, 13, 12.8, 12.4, 14.49, 13.94,
            13.04, 12.5, 14.5, 14.5, 15.5, 15.5, 13.66, 13.2, 12.45, 12, 14.5,
            14.5, 15, 12.16, 11.7, 10.95, 10.5, 10.5, 13, 13, 12.8, 12.4)
)

lok.rec.env <- rbind(
  data.frame(
    month = c(1,1, 3, 4, 5, 7, 8, 8, 9, 10, 11,12),
    day = c(1,15, 15, 15, 15, 1, 1, 15, 15, 15, 15,31),
    variable = "lower",
    value = c(13.5,13.5,12.5, 11.5, 11, 11, 11.5,11.5, 12, 13, 14,14)
  ),
  data.frame(
    month = c(1,1, 3, 4, 5, 6, 8, 9, 9, 10,12),
    day = c(1,15, 15, 1, 1, 15, 15, 1, 15, 15,31),
    variable = "upper",
    value = c(14.5,14.5, 13.5, 13.5, 13, 12, 13, 13.5, 14.5, 15,15)
  )
)

##
vals <- c(-3, -2, -1, 0, 1)
## LORS08
# n_row_vals = nrow(LORS08.sch.bk)
# tot_row = n_row_vals*length(vals)
# date_mat =matrix(NA,nrow=tot_row,ncol=1) # data.frame(Date = rep(NA,tot_row))
# 
# for (i in seq_along(vals)) {
#   start_idx <- (i - 1) * n_row_vals + 1
#   end_idx <- i * n_row_vals
#   date_mat[start_idx:end_idx, 1] <- date.fun(
#     paste(CurWY + vals[i], LORS08.sch.bk$month, LORS08.sch.bk$day, sep = "-")
#   )
# }
# date_mat = data.frame(Date = date.fun(as.POSIXct(date_mat,origin = "1970-01-01")))
# 
# LORS08.sch.bk = cbind(LORS08.sch.bk,date_mat)|>
#   dcast(Date~variable,value.var = "value",mean)|>
#   merge(fill,"Date",all.y=T)
# 
# LORS08.sch.bk[-1] = lapply(LORS08.sch.bk[-1],dat.interp)

## LOSOM effective "2024-08-12"
n_row_vals <- nrow(LOSOM.sch.bk)
tot_row <- n_row_vals*length(vals)
date_mat <- matrix(NA,nrow=tot_row,ncol=1) 

for (i in seq_along(vals)) {
  start_idx <- (i - 1) * n_row_vals + 1
  end_idx <- i * n_row_vals
  date_mat[start_idx:end_idx, 1] <- date.fun(
    paste(CurWY + vals[i], LOSOM.sch.bk$month, LOSOM.sch.bk$day, sep = "-")
  )
}
date_mat <- data.frame(Date = date.fun(as.POSIXct(date_mat,origin = "1970-01-01")))

LOSOM.sch.bk <- cbind(LOSOM.sch.bk,date_mat)|>
  dcast(Date~variable,value.var = "value",mean)|>
  merge(sch_fill,"Date",all.y=T)

LOSOM.sch.bk[-1] <- lapply(LOSOM.sch.bk[-1],dat.interp);

## Recovery Envelope
n_row_vals <- nrow(lok.rec.env)
tot_row <- n_row_vals*length(vals)
date_mat <- matrix(NA,nrow=tot_row,ncol=1) # data.frame(Date = rep(NA,tot_row))
CurWY <- WY(Sys.Date())
for (i in seq_along(vals)) {
  start_idx <- (i - 1) * n_row_vals + 1
  end_idx <- i * n_row_vals
  date_mat[start_idx:end_idx, 1] <- date.fun(
    paste(CurWY + vals[i], lok.rec.env$month, lok.rec.env$day, sep = "-")
  )
}
date_mat <- data.frame(Date = date.fun(as.POSIXct(date_mat,origin = "1970-01-01")))

lok.rec.env.bk <- cbind(lok.rec.env,date_mat)|>
  dcast(Date~variable,value.var = "value",mean)|>
  merge(sch_fill,"Date",all.y=T)
lok.rec.env.bk[-1] <- lapply(lok.rec.env.bk[-1],dat.interp);
lok.rec.env.bk$DOWY <- hydro.day(lok.rec.env.bk$Date)
lok.rec.env.bk$WY <- WY(lok.rec.env.bk$Date)

# LORS08.sch.bk= LORS08.sch.bk|>
#   mutate(DOWY = hydro.day(Date),
#          WY = WY(Date))|>
#   subset(Date<date.fun("2024-08-12"))

LOSOM.sch.bk <- LOSOM.sch.bk|>
  mutate(DOWY = hydro.day(Date),
         WY = WY(Date))|>
  subset(Date>=date.fun("2024-08-12"))

## Lake Okeechobee Stage ------------------------------------------------

stg_da <- readRDS("data/raw/stg_dat.rds")

lok.stg <- subset(stg_da,loc=="LOK")|>
  dcast(Date~Priority,value.var="Data.Value.corr",mean)|>
  mutate(
         WY = WY(Date),
         DOWY = hydro.day(Date),
         DoY = as.numeric(format(Date,"%j")),
         CY = as.numeric(format(Date,"%Y")))

priority_cols <- c("P1", "P2", "P3")
missing_cols <- setdiff(priority_cols, names(lok.stg))

if (length(missing_cols) > 0L) {
  for (cc in missing_cols) {
    lok.stg[[cc]] <- NA_real_
  }
}

lok.stg$Mean <- apply(lok.stg[, priority_cols, drop = FALSE],1,
  function(x) {
    x <- x[!is.na(x)]
    if (length(x) == 0L) NA_real_ else x[1L]
  }
)

lok.stg$Mean[lok.stg$Mean==0]=NA
lok.stg$recess_7day <- with(lok.stg,c(rep(NA,7),diff(Mean,lag=7)))
lok.stg$recess_30day <- with(lok.stg,c(rep(NA,30),diff(Mean,lag=30)))

lok.stg$inter.stage <- dat.interp(lok.stg$Mean)
stg.cat <- c(-Inf,9,10,12,13,15,16,17,Inf)
lok.stg$stg.cat <- as.factor(findInterval(lok.stg$inter.stage,stg.cat))

## Lake Okeechobee Discharge----------------------------------------------
Qdbkeys <- readRDS("data/raw/qdbkeys.rds")
Qdbkeys.melt <- reshape(
  Qdbkeys,
  varying = list(c("DA","BK")),# list(names(Qdbkeys)[2:3]), # columns to melt
  v.names = "DBKEY",                   # name for measurement values
  timevar = "freq",                    # name for the new column holding old col names
  times = c("DA","BK"),# names(Qdbkeys)[2:3],         # actual names from original columns
  direction = "long"
)
row.names(Qdbkeys.melt) <- NULL
Qdbkeys.melt <- subset(Qdbkeys.melt,!is.na(DBKEY))

Qdat <- readRDS("data/raw/Qdat.rds")|>
  merge(Qdbkeys.melt,'DBKEY',all.x=T)

LOKIN <- c("FECSR70","S71","S72","S84","S84X","S65E","S65EX1")
LOKOUT <- c("S77","S354","S351","S352","S271","S308")
lok_sites <- c(LOKIN,LOKOUT)

lok_Qdat <- subset(Qdat,loc%in%lok_sites)|>
  dcast(Date+loc~DA_P,value.var = "Data.Value",mean,na.rm=T)
lok_Qdat$Data.Value <- apply(lok_Qdat[c("P1","P2")], 1, function(x) x[!is.na(x)][1]);# if more P, just add

tom_locs<- Qdbkeys[!(Qdbkeys$DA%in%unique(Qdat$DBKEY)),]

lok_Qdat <- dcast(lok_Qdat,Date~loc,value.var = "Data.Value", fun.aggregate = function(x) mean(cfs.to.acftd(x),na.rm=T))
lok_Qdat[,unique(tom_locs$loc)] <- 0
lok_Qdat[is.na(lok_Qdat)] <- 0; #replace any NAs with 0 

lok_Qdat$LOKIN <- apply(lok_Qdat[,LOKIN],1,sum,na.rm=T)
lok_Qdat$LOKOUT <- apply(lok_Qdat[,LOKOUT],1,sum,na.rm=T)



LOK_flow_dir <- c(FECSR70 = 1,S71 = 1, S72 = 1, S84 = 1, S84X = 1, S65E = 1, S65EX1 = 1,
                  S77 = -1,S354 = -1, S351 = -1, S352 = -1, S271 = -1, S308 = -1)
LOK_Q <- lok_Qdat[,c("Date",names(LOK_flow_dir))]
for (col in names(LOK_flow_dir)) {
  if (col %in% names(LOK_Q)) {
    LOK_Q[[paste0("q", col, ".out")]] <- pmax(0, -LOK_flow_dir[col] * LOK_Q[[col]], na.rm = TRUE)
    LOK_Q[[paste0("q", col, ".in")]]  <- pmax(0, LOK_flow_dir[col] * LOK_Q[[col]], na.rm = TRUE)
  }
}
LOK_Q$LOKIN.kacft <- apply(LOK_Q[,paste0("q",names(LOK_flow_dir),".in")],1,sum,na.rm=T)/1000
LOK_Q$LOKOUT.kacft <- apply(LOK_Q[,paste0("q",names(LOK_flow_dir),".out")],1,sum,na.rm=T)/1000
LOK_Q$EAA_in <- apply(LOK_Q[,paste0("q",c("S354","S351","S352","S271"),".out")],1,sum,na.rm=T)
LOK_Q$NthLake <- apply(LOK_Q[,paste0("q",c("FECSR70","S71","S72","S84","S84X","S65E","S65EX1"),".in")],1,sum,na.rm=T)
## 7day stats
sjudag <- seq(date.fun(as.Date(Sys.Date())-7),date.fun(as.Date(Sys.Date())-1),"1 days")

```

```{r reg sch}
### LORS
LORS08.sch.bk= data.frame(
  day = c(1, 2, 2, 16, 2, 1, 2, 2, 16, 2, 1, 1, 1, 16, 2, 1, 1, 1, 16, 2, 1, 
          16, 16, 1, 16, 1, 1, 1, 16, 1, 16, 1, 16, 1, 2, 1, 1, 16, 1, 16, 1,
          16, 1, 2, 1, 1, 2, 2, 1, 1, 1, 1, 2, 1, 2, 1, 1), 
  month = c(1, 4, 6, 9, 11, 1, 4, 6, 9, 11, 1, 4, 6, 9, 11, 1, 4, 6, 9, 11, 
            1, 2, 4, 6, 9, 10, 12, 1, 2, 4, 4, 6, 9, 10, 11, 12, 1, 2, 4, 4,
            6, 9, 10, 11, 12, 1, 9, 10, 1, 4, 5, 6, 6, 10, 10, 11, 12),
  variable = c("ZONE.B", "ZONE.B", "ZONE.B", "ZONE.B", "ZONE.B", "ZONE.C", 
               "ZONE.C", "ZONE.C", "ZONE.C", "ZONE.C", "ZONE.C1", "ZONE.C1",
               "ZONE.C1", "ZONE.C1", "ZONE.C1", "ZONE.D", "ZONE.D", "ZONE.D", 
               "ZONE.D", "ZONE.D", "ZONE.D0", "ZONE.D0", "ZONE.D0", "ZONE.D0",
               "ZONE.D0", "ZONE.D0", "ZONE.D0", "ZONE.D1", "ZONE.D1", 
               "ZONE.D1", "ZONE.D1", "ZONE.D1", "ZONE.D1", "ZONE.D1",
               "ZONE.D1", "ZONE.D1", "ZONE.D2", "ZONE.D2", "ZONE.D2", 
               "ZONE.D2", "ZONE.D2", "ZONE.D2", "ZONE.D2", "ZONE.D2",
               "ZONE.D2", "ZONE.E", "ZONE.E", "ZONE.E", "ZONE.SSM",
               "ZONE.SSM", "ZONE.SSM", "ZONE.SSM", "ZONE.SSM", "ZONE.SSM",
               "ZONE.SSM", "ZONE.SSM", "ZONE.SSM"), 
  value = c(17.25, 17.25, 16, 16.5, 17.25, 16.88, 16.5, 15.5, 16.13, 16.88, 
            15.25, 14.5, 14, 14.75, 15.25, 16.25, 15.5, 15, 15.75, 16.25, 14,
            13.5, 13.5, 13, 14, 14.5, 14.5, 14.75, 14.29, 14.17, 14.13, 13.67,
            14.58, 14.97, 15.08, 15.08, 15.5, 15.08, 14.83, 14.75, 14.33, 
            15.17, 15.44, 15.67, 15.67, 12.6, 12.6, 13, 12.16, 11.7, 10.95, 
            10.5, 10.5, 13, 13, 12.8, 12.4))  

vals <- c(-3, -2, -1, 0, 1)
fill=data.frame(Date=seq(date.fun(paste(CurWY+min(vals),"01-01",sep="-")),date.fun(paste(CurWY+max(vals),"04-30",sep="-")),"1 days"))

n_row_vals = nrow(LORS08.sch.bk)
tot_row = n_row_vals*length(vals)
date_mat =matrix(NA,nrow=tot_row,ncol=1) # data.frame(Date = rep(NA,tot_row))

for (i in seq_along(vals)) {
  start_idx <- (i - 1) * n_row_vals + 1
  end_idx <- i * n_row_vals
  date_mat[start_idx:end_idx, 1] <- date.fun(
    paste(CurWY + vals[i], LORS08.sch.bk$month, LORS08.sch.bk$day, sep = "-")
  )
}
date_mat = data.frame(Date = date.fun(as.POSIXct(date_mat,origin = "1970-01-01")))

LORS08.sch.bk = cbind(LORS08.sch.bk,date_mat)|>
  dcast(Date~variable,value.var = "value",mean)|>
  merge(fill,"Date",all.y=T)

LORS08.sch.bk[-1] = lapply(LORS08.sch.bk[-1],dat.interp)

LORS08.sch.bk= LORS08.sch.bk|>
  mutate(DOWY = hydro.day(Date),
         WY = WY(Date))|>
  subset(Date<date.fun("2024-08-12"))

### LOSOM
LOSOM.sch.bk = data.frame(
  day = c(1, 2, 2, 2, 1, 2, 2, 1, 2, 2, 1, 1, 1, 1, 2, 1, 2, 1, 1, 1, 1, 1,
          1, 2, 22, 2, 2, 1, 1, 1, 1, 2, 2, 2, 1, 1, 1, 1, 2, 1, 2, 1, 1), 
  month = c(1, 4, 6, 11, 1, 6, 11, 1, 6, 11, 1, 4, 5, 6, 6, 10, 10, 11, 12,
            1, 4, 5, 6, 6, 8, 10, 11, 1, 4, 5, 6, 6, 10, 11, 1, 4, 5, 6, 6,
            10, 10, 11, 12), 
  variable = c("ZONE.A", "ZONE.A", "ZONE.A", "ZONE.A", "ZONE.BC", "ZONE.BC", 
               "ZONE.BC",  "ZONE.BXX", "ZONE.BXX", "ZONE.BXX", "ZONE.D",
               "ZONE.D", "ZONE.D",  "ZONE.D", "ZONE.D", "ZONE.D", "ZONE.D",
               "ZONE.D", "ZONE.D", "ZONE.D1",  "ZONE.D1", "ZONE.D1", "ZONE.D1", 
               "ZONE.D1", "ZONE.D1", "ZONE.D1", "ZONE.D1", "ZONE.D2", 
               "ZONE.D2", "ZONE.D2", "ZONE.D2", "ZONE.D2", "ZONE.D2",
               "ZONE.D2", "ZONE.D3", "ZONE.D3", "ZONE.D3", "ZONE.D3",
               "ZONE.D3", "ZONE.D3", "ZONE.D3", "ZONE.D3", "ZONE.D3"), 
  value = c(17.25, 17.25, 16.5, 17.25, 16.85, 16.1, 16.85, 16.85, 16.1, 16.85,
            12.16,  11.7, 10.95, 10.5, 10.5, 13, 13, 12.8, 12.4, 14.49, 13.94,
            13.04, 12.5, 14.5, 14.5, 15.5, 15.5, 13.66, 13.2, 12.45, 12, 14.5,
            14.5, 15, 12.16, 11.7, 10.95, 10.5, 10.5, 13, 13, 12.8, 12.4)
)

n_row_vals = nrow(LOSOM.sch.bk)
tot_row = n_row_vals*length(vals)
date_mat =matrix(NA,nrow=tot_row,ncol=1) # data.frame(Date = rep(NA,tot_row))

for (i in seq_along(vals)) {
  start_idx <- (i - 1) * n_row_vals + 1
  end_idx <- i * n_row_vals
  date_mat[start_idx:end_idx, 1] <- date.fun(
    paste(CurWY + vals[i], LOSOM.sch.bk$month, LOSOM.sch.bk$day, sep = "-")
  )
}
date_mat = data.frame(Date = date.fun(as.POSIXct(date_mat,origin = "1970-01-01")))

LOSOM.sch.bk = cbind(LOSOM.sch.bk,date_mat)|>
  dcast(Date~variable,value.var = "value",mean)|>
  merge(fill,"Date",all.y=T)

LOSOM.sch.bk[-1] = lapply(LOSOM.sch.bk[-1],dat.interp);

LOSOM.sch.bk = LOSOM.sch.bk|>
  mutate(DOWY = hydro.day(Date),
         WY = WY(Date))|>
  subset(Date>=date.fun("2024-08-12"))


## Recovery Envelope
lok.rec.env <- rbind(
  data.frame(
    month = c(1,1, 3, 4, 5, 7, 8, 8, 9, 10, 11,12),
    day = c(1,15, 15, 15, 15, 1, 1, 15, 15, 15, 15,31),
    variable = "lower",
    value = c(13.5,13.5,12.5, 11.5, 11, 11, 11.5,11.5, 12, 13, 14,14)
  ),
  data.frame(
    month = c(1,1, 3, 4, 5, 6, 8, 9, 9, 10,12),
    day = c(1,15, 15, 1, 1, 15, 15, 1, 15, 15,31),
    variable = "upper",
    value = c(14.5,14.5, 13.5, 13.5, 13, 12, 13, 13.5, 14.5, 15,15)
  )
)

n_row_vals <- nrow(lok.rec.env)
tot_row <- n_row_vals*length(vals)
date_mat <- matrix(NA,nrow=tot_row,ncol=1) # data.frame(Date = rep(NA,tot_row))
CurWY <- WY(Sys.Date())
for (i in seq_along(vals)) {
  start_idx <- (i - 1) * n_row_vals + 1
  end_idx <- i * n_row_vals
  date_mat[start_idx:end_idx, 1] <- date.fun(
    paste(CurWY + vals[i], lok.rec.env$month, lok.rec.env$day, sep = "-")
  )
}
date_mat <- data.frame(Date = date.fun(as.POSIXct(date_mat,origin = "1970-01-01")))

lok.rec.env.bk <- cbind(lok.rec.env,date_mat)|>
  dcast(Date~variable,value.var = "value",mean)|>
  merge(sch_fill,"Date",all.y=T)
lok.rec.env.bk[-1] <- lapply(lok.rec.env.bk[-1],dat.interp);
lok.rec.env.bk$DOWY <- hydro.day(lok.rec.env.bk$Date)
lok.rec.env.bk$WY <- WY(lok.rec.env.bk$Date)

```

```{r STG_STORE}
WCP.tab7_8 <- data.frame(
  STG.FT = c(8, 8.1, 8.2, 8.3, 8.4, 8.5, 8.6, 8.7, 8.8, 8.9, 9, 9.1, 9.2, 
             9.3, 9.4, 9.5, 9.6, 9.7, 9.8, 9.9, 10, 10.1, 10.2, 10.3, 10.4,
             10.5, 10.6, 10.7, 10.8, 10.9, 11, 11.1, 11.2, 11.3, 11.4, 11.5,
             11.6, 11.7, 11.8, 11.9, 12, 12.1, 12.2, 12.3, 12.4, 12.5, 12.6,
             12.7, 12.8, 12.9, 13, 13.1, 13.2, 13.3, 13.4, 13.5, 13.6, 13.7, 
             13.8, 13.9, 14, 14.1, 14.2, 14.3, 14.4, 14.5, 14.6, 14.7, 14.8, 
             14.9, 15, 15.1, 15.2, 15.3, 15.4, 15.5, 15.6, 15.7, 15.8, 15.9, 
             16, 16.1, 16.2, 16.3, 16.4, 16.5, 16.6, 16.7, 16.8, 16.9, 17, 
             17.1, 17.2, 17.3, 17.4, 17.5, 17.6, 17.7, 17.8, 17.9, 18, 18.1,
             18.2, 18.3, 18.4, 18.5, 18.6, 18.7, 18.8, 18.9, 19, 19.1, 19.2, 
             19.3, 19.4, 19.5, 19.6, 19.7, 19.8, 19.9, 20),
  STORE.ACFT = c(1329506 , 1356107 , 1382985 , 1410137 , 1437563 , 1465259 , 
                 1493225 , 1521460 , 1549960 , 1578726 , 1607755 , 1637045 , 
                 1666596 , 1696405 , 1726471 , 1756792 , 1787366 , 1818193 , 
                 1849270 , 1880596 , 1912169 , 1943988 , 1976050 , 2008355 , 
                 2040901 , 2073686 , 2106708 , 2139967 , 2173459 , 2207185 , 
                 2241141 , 2275328 , 2309742 , 2344382 , 2379247 , 2414335 ,
                 2449644 , 2485174 , 2520921 , 2556886 , 2593065 , 2629458 ,
                 2666063 , 2702878 , 2739901 , 2777132 , 2814567 , 2852207 , 
                 2890049 , 2928092 , 2966333 , 3004772 , 3043407 , 3082235 , 
                 3121257 , 3160469 , 3199871 , 3239460 , 3279235 , 3319195 , 
                 3359338 , 3399662 , 3440166 , 3480848 , 3521707 , 3562740 , 
                 3603947 , 3645325 , 3686873 , 3728590 , 3770474 , 3812523 , 
                 3854735 , 3897110 , 3939644 , 3982338 , 4025189 , 4068196 ,
                 4111356 , 4154669 , 4198133 , 4241745 , 4285506 , 4329412 , 
                 4373463 , 4417656 , 4461990 , 4506464 , 4551076 , 4595825 , 
                 4640708 , 4685724 , 4730871 , 4776149 , 4821554 , 4867087 , 
                 4912744 , 4958525 , 5004428 , 5050450 , 5096592 , 5142851 , 
                 5189225 , 5235712 , 5282312 , 5329023 , 5375843 , 5422770 ,
                 5469802 , 5516939 , 5564179 , 5611519 , 5658959 , 5706497 ,
                 5754130 , 5801858 , 5849680 , 5897592 , 5945594 , 5993684 ,
                 6041861 ))

get_LOK_volume <- approxfun(WCP.tab7_8$STG.FT, WCP.tab7_8$STORE.ACFT, rule = 2) # Stage -> Volume


lok.stg$store_vol_kacft <- get_LOK_volume(lok.stg$Mean)/1000
lok.stg$diff_store <- c(NA,diff(lok.stg$store_vol_kacft))

```

## Regulation Schedule

```{r echo=F}
LOSOM.sch.bk2 <-  LOSOM.sch.bk[,c("Date","ZONE.A","ZONE.BC","ZONE.D")]|>
  melt(id.var = "Date",value.name="reg.STG",variable.name="Zone")|>
  merge(data.frame(Zone=c("ZONE.A","ZONE.BC","ZONE.D"),
                   Zone.txt = c("Zone A","Zone BC","Zone D")),
        "Zone")
tmp.dat  <-  subset(lok.stg,Date==YEST)
tmp.sch  <-  subset(LOSOM.sch.bk2,Date == YEST)

zone_order <- c("ZONE.A", "ZONE.BC", "ZONE.D")
tmp.sch <- tmp.sch[order(match(tmp.sch$Zone, zone_order)), ]
stage <- tmp.dat$Mean
idx <- which(stage >= tmp.sch$reg.STG)[1]

# If stage is below all zone floors, compare against the lowest floor
if (is.na(idx)) {
  idx <- which.min(tmp.sch$reg.STG)
}

zone.txt.val <- tmp.sch$Zone.txt[idx]
zone.diff <- stage - tmp.sch$reg.STG[idx]

zone.diff.txt <- format(round(abs(zone.diff), 1), nsmall = 1)

if (zone.diff >= 0) {
  zone.statement <- paste0(zone.diff.txt, " ft above ", zone.txt.val, " floor")
} else {
  zone.statement <- paste0(zone.diff.txt, " ft below ", zone.txt.val, " floor")
}

get_reg_zone <- function(stage, sch_day,
                         zone_order = c("ZONE.A", "ZONE.BC", "ZONE.D"),
                         digits = 1) {
  
  sch_day <- sch_day[order(match(sch_day$Zone, zone_order)), ]
  
  idx <- which(stage >= sch_day$reg.STG)[1]
  
  if (is.na(idx)) {
    idx <- which.min(sch_day$reg.STG)
  }
  
  diff_ft <- stage - sch_day$reg.STG[idx]
  
  relation <- if (diff_ft >= 0) "above" else "below"
  
  data.frame(
    Zone = sch_day$Zone[idx],
    Zone.txt = sch_day$Zone.txt[idx],
    stage = stage,
    reg.STG = sch_day$reg.STG[idx],
    diff_ft = diff_ft,
    diff_ft_rounded = round(diff_ft, digits),
    statement = paste0(
      format(round(abs(diff_ft), digits), nsmall = digits),
      " ft ",
      relation,
      " ",
      sch_day$Zone.txt[idx]# ," floor"
    )
  )
}

lok_zone_calc <- get_reg_zone(subset(lok.stg,Date==YEST)$Mean,
                               subset(LOSOM.sch.bk2,Date == YEST),
                               zone_order = c("ZONE.A", "ZONE.BC", "ZONE.D"))

```

For details on the current Lake Okeechobee Regulation Schedule, please refer to the Lake Okeechobee System Operating Manual Water Control Plan ([LOSOM WCP](./_docs/2024_LOSOM_WCP.pdf)).

Currently, Lake Okeechobee is `r paste0(lok_zone_calc$statement)` of the LOSOM regulation schedule. The current average lake stage is `r paste0(format(lok_zone_calc$stage,nsmall = 2)," Ft NGVD29")`.


```{r table1, fig.align='center'}
#| tbl-cap-location: top
#| tbl-cap: "Stage and recession rates this time for the current and last three water years"
# cap.val="Stage and recession rates this time for the current and last three water years"

subset(lok.stg,DOWY==hydro.day(YEST)&WY>=CurWY-3)|>
  flextable(col_keys=c("Date","WY","Mean","recess_7day","recess_30day"))|>
  width(width=c(1,1,1.25,1.5,1.5))|>
  align(align="center",part="all")|>
  colformat_datetime(j=1,fmt_date="%m-%d")|>
  colformat_double(j=2,big.mark="",digits=0)|>
  colformat_num(j=3:5,na_str="- NR -")|>
  padding(padding=1,part="all")|>
  # font(fontname="Times New Roman",part="all")|>
  fontsize(size=12,part="body")|>
  fontsize(size=13,part="header")|>
  bold(part="header")|>
  set_header_labels("DATE"="Date\n(Month-Day)",
                    "WY"="Water Year",
                    "Mean"="Stage\n(ft, NGVD29)",
                    "recess_7day"="7-Day Recession Rate\n(ft 7-d\u207B\u00B9)",
                    "recess_30day"="30-Day Recession Rate\n(ft 30-d\u207B\u00B9)")|>
  bg(i=~WY==CurWY,part="body",bg="wheat")
  # add_header_lines(values=cap.val)|>align(align="center",part="header")|>fontsize(size=13,part="header")# |>
  # footnote(i=4,j=3,value=ifelse(is.na(subset(LakeO.xtab,DATE==YEST)$P1)==T|is.na(subset(LakeO.xtab,DATE==YEST)$P2)==T,as_paragraph("Value estimated from average stage height across L001, L005, L006, LZ40, S133TW, S352HW & S4TW"),as_paragraph("Value provided by SFWMD DBKEY:N3466")),ref_symbols =c(" A "))|>
  # footnote(j=5,part="header",value=as_paragraph("-0.5 ft 30-d\u207B\u00B9 maximum 30-day Recession Rate for HAB Deviation"),ref_symbols =c(" B "))
```

```{r LORSplot,results='hide',dpi=96,fig.width=7,fig.height=4.75,fig.align='center',fig.cap=paste0("Lake Okeechobee daily average stage elevation for water year ",CurWY," (WY", CurWY,") relative to the last two water years relative to the Lake Okeechobee Regulation Schedule (LORS).")}

lwd.val <- 1
xlim.vals <- date.fun(c(paste(CurWY-1,05,01,sep="-"),paste(CurWY,04,30,sep="-")))
xmaj <- seq(xlim.vals[1],xlim.vals[2],by="2 months");xmin <- seq(xlim.vals[1],xlim.vals[2],by="1 months")
xlim.vals2 <- hydro.day(xlim.vals)

ylim.val <- c(9,18);by.y <- 1
ymaj <- seq(ylim.val[1],ylim.val[2],by.y);ymin <- seq(ylim.val[1],ylim.val[2],by.y/2)

par(mar=c(0.5,1.5,1,1.5),oma=c(0.5,3,1,3));
layout(matrix(1:2,2,1,byrow=T),heights=c(1,0.25))

plot(ZONE.BC~DOWY,LOSOM.sch.bk,ylim=ylim.val,xlim=xlim.vals2,type="n",ann=F,axes=F,yaxs="i",xaxs="i")
abline(h=seq(9,18,1),v=hydro.day(xmin),lwd=1,col="grey",lty=3)
if(RecEnv.plot==1){with(subset(lok.rec.env.bk,WY==CurWY),shaded.range(DOWY,lower,upper,"grey60",col.adj=1,lty=1))}
with(subset(LOSOM.sch.bk,WY==CurWY),lines(ZONE.A~DOWY,lwd=2,col="black"))
with(subset(LOSOM.sch.bk,WY==CurWY),lines(ZONE.BC~DOWY,lwd=2,col="black"))
with(subset(LOSOM.sch.bk,WY==CurWY),lines(ZONE.D~DOWY,lwd=2,col="grey"))
text(246,17.5,"Zone A",font=2)
text(290,16.8,"Zone BC",font=2,pos = 4)
text(277,14.3,"Zone D",font=2,pos = 4)
for(i in seq_along(lok_stage_yrs)){
lines(Mean ~ DOWY,subset(lok.stg, WY == lok_stage_yrs[i]),lwd = 3, col = lok_stage_cols[i], lty = 1)
}

lab.loc <- subset(LOSOM.sch.bk,Date == YEST)$ZONE.D-0.8

yest_dat <- subset(lok.stg, Date == YEST)

if (nrow(yest_dat) > 0 && !is.na(yest_dat$Mean)) {
  points(Mean ~ DOWY, yest_dat,pch = 21, bg = adjustcolor("grey", 0.5), col = "gray", lwd = 0.1, cex = 1.25)
  # Extract values once
  DOWY_val <- yest_dat$DOWY
  Mean_val <- yest_dat$Mean
  if (DOWY_val > 300) {
    segments(DOWY_val, Mean_val, DOWY_val - 30, lab.loc, lty = 2)
    text(DOWY_val - 30, lab.loc,
         paste(format(round(Mean_val, 2), nsmall = 2), "Ft\nNGVD29"),
         cex = 0.8, xpd = NA, pos = 1, offset = -0.1)
  } else if (DOWY_val < 30) {
    segments(DOWY_val, Mean_val, DOWY_val + 30, lab.loc, lty = 2)
    text(DOWY_val + 30, lab.loc + 0.1,
         paste(format(round(Mean_val, 2), nsmall = 2), "Ft\nNGVD29"),
         cex = 0.8, xpd = NA, pos = 1, offset = 0.1)
  } else {
    segments(DOWY_val, Mean_val, DOWY_val, lab.loc, lty = 2)
    text(DOWY_val, lab.loc + 0.1,
         paste(format(round(Mean_val, 2), nsmall = 2), "Ft\nNGVD29"),
         cex = 0.8, xpd = NA, pos = 1, offset = 0.1)
  }
}
axis_fun(1,hydro.day(xmaj),hydro.day(xmin),format(xmaj,"%b"),line=-0.5)
axis_fun(2,ymaj,ymin,ymaj)
box(lwd=1)
mtext(side=1,"Month",line=2,cex=1.25)
mtext(side=2,"Stage Elevation (Feet, NGVD29)",line=2.5,cex=1.25)
mtext(side=3,adj=0,paste("Date:",format(date.fun(as.Date(Sys.Date())),"%b %d, %Y")))
mtext(side=3,adj=1,"Data are provisional and subject to change",col="red")

ylim.val2=c(8,16);by.y2=1
ymaj2=seq(ylim.val2[1],ylim.val2[2],by.y2);ymin2=seq(ylim.val2[1],ylim.val2[2],by.y2/2)
lok.con=1.25
axis_fun(4,ymaj2+lok.con,ymin2+lok.con,ymaj2)
mtext(side=4,"Stage Elevation (Feet, NAVD88)",line=2.5,cex=1.25)

plot(0:1,0:1,type = 'n', axes = F,xlab=NA, ylab=NA)
legend(0.5,0.5,
       legend=c(paste0("WY",rev(lok_stage_yrs))),
       col=rev(lok_stage_cols),lty=c(1,1),lwd=c(4,4,4),ncol=2,cex=1,bty="n",y.intersp=1,x.intersp=0.5,xpd=NA,xjust=0.5)

```

```{r LOK stage calendar,echo=FALSE,fig.width=6,fig.height=5,fig.align='center',fig.cap="Lake Okeechobee stage calendar plot from 2008 to current." }
xlabs <- seq(date.fun("2025-05-01"),date.fun("2026-04-30"),"1 months")
xlabs.nums <- hydro.day(xlabs)
xlabs.labs <- format(xlabs,"%b")

cols <- viridis::turbo(length(stg.cat)-1,direction = -1)
ggplot(lok.stg, aes(x = DOWY, y = WY, fill = stg.cat)) +
  geom_tile(aes(group = stg.cat), colour = NA)+
  scale_y_reverse(expand = c(0, 0), breaks = unique(lok.stg$WY)) +
  scale_x_continuous(expand = c(0, 0),
                     limits = c(1,365),
                     breaks = xlabs.nums,
                     labels = xlabs.labs)+
  scale_fill_manual(values = cols,
                    name="Lake Stage Category\n(Ft, NGVD29)",
                    breaks=seq(1,length(stg.cat)-1,1),
                    labels=c("< 9","9 - 10", "10 - 12", "12 - 13","13 - 15", "15 - 16","16 - 17", "> 17")) +
  # theme_bw(base_family = "serif") +
  labs(title = "Lake Okeechobee",
       subtitle = "Stage Elevation",
       caption = paste0("Produced: ",format(Sys.Date(),"%d %b %Y")),
       x="Day of Water Year",
       y="Water Year")

```


## Discharge

```{r LOK_Q,dev="png", echo=FALSE,fig.width=6,fig.height=4.5,fig.align='center',fig.cap="Total Lake Okeechobee inflow and outflow volume for measured inflow/ouflows. Data Source: SFWMD DBHydro ."}

max.q <- subset(LOK_Q,Date%in%seq(date.fun(as.Date(End.Date)-30),date.fun(as.Date(End.Date)+3),"1 days"))[,c("LOKIN.kacft","LOKOUT.kacft")]|>
  max(na.rm=T)

ylim.max <- ceiling(max.q*1.5)
ylim.val <- c(0,ylim.max);
ymaj <- heckbert_labs(ylim.val[1],ylim.val[2],5)
ymin <- seq(ylim.val[1],ylim.val[2],min(diff(ymaj))/2)
# by.y <- ylim.max/4;ymaj <- seq(ylim.val[1],ylim.val[2],by.y);ymin=seq(ylim.val[1],ylim.val[2],by.y/2)
xlim.val <- date.fun(c(as.Date(End.Date)-30,as.Date(End.Date)+3));xmaj <- seq(xlim.val[1],xlim.val[2],by="7 days");xmin <- seq(xlim.val[1],xlim.val[2],by="1 days")


layout(matrix(1:2,2,1,byrow=F),heights=c(2,0.4))
par(mar=c(2,2,1,1),oma=c(0.5,2,1,2));
plot(LOKIN.kacft~Date,LOK_Q,type="n",ylim=ylim.val,xlim=xlim.val,xaxs="i",yaxs="i",xaxt="n",yaxt="n",xlab=NA,ylab=NA)
abline(h=ymaj,v=xmaj,lty=3,col="grey")
lines(LOKIN.kacft~Date,LOK_Q,col=Q_cols[1],lwd=2)
lines(LOKOUT.kacft~Date,LOK_Q,col=Q_cols[2],lwd=2,lty=2)
axis_fun(1,xmaj,xmin,format(xmaj,"%m-%d"),line=-0.5)
axis_fun(2,ymaj,ymin,format(ymaj),cex.axis=1)
box(lwd=1)
mtext("Date (MM-DD)",side=1,line=2,cex=1)
mtext(expression("Daily Discharge (x1000 Ac-Ft d"^" -1"*")"),side=2,line=2,cex=1)

plot(0:1,0:1,type="n",yaxt="n",xaxt="n",bty="n")
legend(0.5,0.5,
       legend=c("Lake Inflow","Lake Outflow"),
       col=Q_cols,lty=c(1,2),lwd=c(2.5,2.5),pt.cex=2.5,ncol=2,cex=1,bty="n",y.intersp=1,x.intersp=0.5,xpd=NA,xjust=0.5)

```

```{r table2,fig.align='center' }
#| tbl-cap-location: top
#| tbl-cap: "Inflow, outflow, storage and change in storage for the past 7-days."
# cap.val="Total measure inflow and outflow discharge volume, predicted lake storage volume and the change in store from the previous day."

merge(lok.stg,LOK_Q,
      by.x=c("Date"),
      by.y = c("Date"))|>
  subset(Date%in%seq(date.fun(as.Date(YEST)-7),YEST,"1 days"))|>
  flextable(col_keys = c("Date","Mean","LOKIN.kacft","LOKOUT.kacft","store_vol_kacft","diff_store"))|>
  colformat_datetime(j=1,fmt_datetime = "%Y-%m-%d")|>
  colformat_double(j=c(2:4,6),digits=2)|>
  colformat_double(j=5,digits=0,big.mark = "")|>
  align(align="center",part="all")|>
  padding(padding=1,part="all")|>
  fontsize(size=12,part="body")|>
  fontsize(size=13,part="header")|>
  bold(part="header")|>
  width(width = c(1,1.2,1,1,1,1))|>
  set_header_labels("Mean" = "Lake Stage\n(Ft, NGVD29)",
                    "LOKIN.kacft"="Measured Inflow\n(kAcft d\u207B\u00B9)",
                    "LOKOUT.kacft"="Measured Outflow\n(kAcft d\u207B\u00B9)",
                    "store_vol_kacft" = "Estimated\nStorage Volume (kAcft)",
                    "diff_store" = "\u0394 Storage (kAcft)")|>
  footnote(j="LOKIN.kacft",part="header",
           value=as_paragraph("Aggregated from ",paste(LOKIN,collapse = ", ")),ref_symbols =c(" A "))|>
  footnote(j="LOKOUT.kacft",part="header",
           value=as_paragraph("Aggregated from ",paste(LOKOUT,collapse = ", ")),ref_symbols =c(" B "))|>
  footnote(j="store_vol_kacft",part="header",
           value=as_paragraph("Estimated storage volume based Stage-Volume relationship presented in Table 7-8 of LOSOM WCP."),ref_symbols =c(" C "))

```

*Page rendered: `r format(Sys.time(), "%b %d, %Y %H:%M %Z")` &nbsp;•&nbsp; Data through: `r format(YEST, "%b %d, %Y")`*

***